Parallelization of Fast $\ell_1$-Minimization for Face Recognition

### 2011-03-29 main.tex
Added diagram showing caches

@@

The first experiment compares the performance of our two proposed implementations of 
the general $\ell_1$-minimization problem (Algorithm \eqref{alg:alm}) given a generic random matrix $A$ and a random sparse
vector $\xx_0$.  
The measurement $d \times n$ matrix $A$ was generated as a random Gaussian matrix, with each entry
randomly generated from the standard normal and normalized with unit column norm.  The ratio of $d:n$ varied from
$1:10$ to $5:10$ with $n$ varying from 500 to 8000.
The ground truth signals, $\xx_0$ had a sparsity rate of 0.1 with elements generated using the standard normal and also normalized with unit norm.
Because the ground truth signal $\xx_0$ was known, the algorithm terminated
when $\|\bx-\bx_0\| < \tau$.
The measurement vector was generated with the equation $\b_0 = A \x_0$.

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=3.5in]{figures/caches}
\end{center}
\caption{Scale Drawing of the CPU and GPU cache sizes}
\label{fig:caches}
\end{figure}

@@

The first experiment compares the performance of our two proposed implementations of 
the general $\ell_1$-minimization problem (Algorithm \eqref{alg:alm}) by
comparing the amount of time to solve a problem given a generic random matrix $A$ and a random sparse
vector $\xx_0$.  
The measurement $d \times n$ matrix $A$ was generated as a random Gaussian matrix, with each entry
randomly generated from the standard normal and normalized with unit norm.  The ratio of $d:n$ varied from
$10:1$ to $10:5$ with $d$ varying from 500 to 8000.
The ground truth signals, $\xx_0$ had a sparsity rate of 0.1 with elements generated using the standard normal and normalized with unit norm.
Because the ground truth signal $\xx_0$ was known, the algorithm terminated
when $norm(\bx-\bx_0) < tolerance$.
The measurement vector was generated with the equation $\y_0 = A \x_0$.
